---
title: "prepackR"
author: "Jingyun Chen, Anthony Chiodo, Sarah Watts"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Welcome to prepackR! This function will allow you to perform some basic data cleaning/processing tasks. The information below will walk you through the functionality of this package.

Step 1, load the package.

```{r}
library(prepackR)
```

Now that the package is loaded, you will have access to three functions.     

1. stdizer - a function that allows you to standardize a dataset     
2. na_counter - a function that allows you to count the number of na values in dataset     
3. splitter - a function that allows you to split a dataset into training and testing

Let's start with the stdizer function!

```{r}
# Load gapminder data set
df <- gapminder::gapminder

# Scale gdpPercap
df_scaled <- stdizer(X = df, col_index = c(6), method = 'mean_sd')
```

Now let's take a look at the na_counter function.

```{r}
# Setup sample dataset 
Name <- c("Sam", "Tim", NA)
Sex <- c("women", "men", "women")
Age <- c(55, 62, NA)
dt <- data.frame(Name, Sex, Age)

# Count NAs in sample dataset
na_count <- na_counter(dt)
```

Finally, let's look at the splitter function.

```{r}
# Load gapminder data set
df <- gapminder::gapminder

# Split gapminder
split_data <- splitter(df, 1, split_size = 0.8, seed=42)
```
